Hydra Battles and Cie

### 2021-08-04 doc/part-hydras.tex
converting chapter 3 to alectryon (continued)

\begin{Coqsrc}
Lemma limit_iff (alpha : t) : Limit alpha <-> alpha = omega.
\end{Coqsrc}

Regarding successors, let us define the following function:

\begin{Coqsrc}
Definition succ (alpha : t) :=
  match alpha with
    inl n => inl (S n)
  | inr n => inr (S n)
  end.
\end{Coqsrc}

\begin{Coqsrc}
Lemma Successor_correct alpha beta : Successor beta alpha <->
                                     beta = succ alpha.
\end{Coqsrc}

We can also check whether an ordinal is a successor by a simple pattern matching:

\begin{Coqsrc}
  Definition succb (alpha: t) : bool :=
  match alpha with
  | inr (S  _) | inl (S _) => true
  | _ => false
  end.

Lemma succb_correct (alpha : t) :
    succb alpha <->  exists beta: t, alpha = succ beta.
\end{Coqsrc}

@@

\noindent\emph{From Module~\href{../theories/html/hydras.OrdinalNotations.ON_Generic.html}{ON\_Generic}}
\begin{Coqsrc}
  Definition ZeroLimitSucc_dec {A:Type}{lt: relation A}
           {compare : A -> A -> comparison}
           {on : ON lt compare} :=
  forall alpha,
    {Least alpha} +
    {Limit alpha} +
    {beta: A | Successor alpha beta}.
(* ... *)
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition Zero_limit_succ_dec : ZeroLimitSucc_dec.
Proof.
(* ... *)
Defined.
\end{Coqsrc}

@@

@@

\begin{Coqsrc}
Section Defs.

  Context `(ltA: relation A)
          (compareA : A -> A -> comparison)
          (NA: ON ltA compareA).
  Context `(ltB: relation B)
          (compareB : B -> B -> comparison)
          (NB: ON ltB compareB).

Definition t := (B * A)%type.
Definition lt : relation t := lexico ltB ltA.

Definition compare (alpha beta: t) : comparison :=
  match compareB (fst alpha) (fst beta) with
  | Eq => compareA (snd alpha) (snd beta)
  | c => c
  end.

#[global] Instance ON_mult: ON lt compare.

End Defs.
\end{Coqsrc}

@@

\begin{Coqsrc}
Instance Omega2: ON _ _ := ON_mult Omega Omega.

Definition t := ON_mult.t nat nat.
\end{Coqsrc}

\begin{Coqsrc}
Definition zero: t := (0,0).

Definition fin (n:nat) : t := (0, n).

Coercion fin : nat >-> t.

Notation omega := (1,0).

Definition limitb (alpha : t) : bool := 
 match alpha with
 |  (S _, 0) => true
 | _ => false
 end.

 Definition succb (alpha: t) : bool :=
 match alpha with
  (_, S _) => true
  | _ => false
end.
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition succ (alpha : t) := (fst alpha, S (snd alpha)).
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma succ_ok alpha beta : Successor beta alpha <-> beta = succ alpha.
\end{Coqsrc}

\begin{Coqsrc}
Lemma lt_succ_le alpha beta : alpha o< beta <-> succ alpha o<= beta.

Lemma lt_succ alpha : alpha o< succ alpha.

>>>>

\input{movies/snippets/ON_Omega_plus_omega/limitIff}

Regarding successors, let us define the following function and prove its correctness:

\input{movies/snippets/ON_Omega_plus_omega/succDef}

\input{movies/snippets/ON_Omega_plus_omega/succCorrect}

We can also check whether an ordinal is a successor by a simple computation:

\input{movies/snippets/ON_Omega_plus_omega/succb}

@@

@@

\input{movies/snippets/ON_Omega_plus_omega/ZeroLimitSuccDec}

@@

In \coq{}, we build an instance of class \texttt{ON} through a sequence of steps as for the sum of ordinal notations.

@@

\input{movies/snippets/ON_mult/Defs}

@@

\input{movies/snippets/ON_Omega2/Omega2Def}

\input{movies/snippets/ON_Omega2/Defs}

@@

\input{movies/snippets/ON_Omega2/Defs}

@@

\input{movies/snippets/ON_Omega2/succOK}

\input{movies/snippets/ON_Omega2/succLemmas}
